---
title: "R Day 3"
author: "Angela Chen"
date: "9/19/2018"
output: html_document
---

```{r setup, include=FALSE}
generation<-read.csv(here::here("data","generation.csv"),stringsAsFactors = F)
imports<-read.csv(here::here("data","imports.csv"),stringsAsFactors = F)
library(lubridate)
generation$datetime<-as_datetime(generation$datetime)
head(generation$datetime)
imports$datetime<-as_datetime(imports$datetime)
head(imports$datetime)
```
class(generation$datetime)
head(generation$datetime)

```{r}
library(reshape2)
long_gen<-melt(generation,id.vars="datetime",variable.name="source",value.name = "usage")

```

head(long_gen)
long_gen[order(long_gen$datetime)[1:20],]

```{r}
merged_energy<-merge(generation,imports,by="datetime")
```
dim(merged_energy)

```{r}
long_merged_energy<-melt(merged_energy,id.vars="datetime",variable.name = "source",value.name = "usage")
```
head(long_merged_energy)

library(dplyr)
tmp<-select(merged_energy,biogas,biomass,geothermal,solar)
tmp<-filter(merged_energy,imports>7000)
tmp <- mutate(long_merged_energy, log_usage = log(usage))
names(tmp)
head(tmp)

summarize(long_merged_energy, total = sum(usage, na.rm = T))

long_merged_energy %>% 
  filter(source == "geothermal") %>% 
  select(-datetime) %>% 
  mutate(log_usage = log(usage)) %>% 

merged_energy %>% 
  select(-datetime) %>% 
  mutate(total_usage = rowSums(., na.rm = T)) %>% 
summarize(total_usage = sum(total_usage, na.rm = T))
summarize(mean_log_usage = mean(log_usage, na.rm = T))

```{r}
merged_energy %>%
select(contains("hydro")) %>%
mutate(total_hydro=rowSums(.,na.rm=T)) %>%
summarize(mean_hydro=mean(total_hydro,na.rm=T))
```

```{r}
long_merged_energy%>%
  group_by(source)%>%
  summarise(sum_usage=sum(usage,na.rm=T))
```

```{r}
merged_energy %>%
  select(datetime,contains("hydro"),starts_with("bio")) %>%
  melt(id.vars="datetime",variable.name="source",value.name = "usage")%>%
  group_by(source)%>%
  summarize(mean_usage=mean(usage,na.rm = T))
```

